Hydra Battles and Cie

### 2021-01-24 doc/part-hydras.tex
add an exercise
add partial solutions to exercises

\index{Exercises}
\begin{exercise}
Prove, that, in any ordinal notation system, if $\beta$ is a successor of $\alpha$,
then for any $\gamma$, $\gamma<\beta$ implies 
$\gamma\leq\alpha$.
\end{exercise}

@@

\index{Exercises}
 \begin{exercise}
Prove in \coq{} that for any ordinal $\alpha<\epsilon_0$, $\alpha$ is a limit if 
and only if for all $\beta<\alpha$, the interval $[\beta,\alpha)$ is infinite.
 \end{exercise}

>>>>

\index{Exercises}
\begin{exercise}
Prove, that, in any ordinal notation system, if $\beta$ is a successor of $\alpha$,
then for any $\gamma$, $\gamma<\beta$ implies 
$\gamma\leq\alpha$.

\emph{You may start this exercise with the file
\url{../exercises/ordinals/lt_succ_le.v}.}
\end{exercise}

@@

\index{Exercises}
 \begin{exercise}
Prove in \coq{} that for any ordinal $0< \alpha<\epsilon_0$, $\alpha$ is a limit if 
and only if for all $\beta<\alpha$, the interval $[\beta,\alpha)$ is
infinite.

\emph{You may start this exercise with the file
\url{../exercises/ordinals/Limit_Infinity.v}.}
 \end{exercise}
